---
title: "hw - 07 README"
author: "Javier Castillo-Arnemann"
output: github_document
---

This is a repository containing the 2nd assignment of the **STAT 547** course. The course main page can be found [here](http://stat545.com/Classroom). The instructions for this assignment can be accesed [here](http://stat545.com/Classroom/assignments/hw07/hw07.html).


##Package Information
For this homework I created a new data package called `sportsPolitics` that uses data from [FiveThirtyEight](https://fivethirtyeight.com/), a great politics, economics and sports blog that employs data analysis for all their articles. This dataset was used in their [How Every NFL Team's Fans Lean Politically](https://fivethirtyeight.com/features/how-every-nfl-teams-fans-lean-politically/) article, and summarizes the Google Trends results for Google searches of major sports in the US (NFL, MLB, NHL, NBA, College Football (CFB) and College Baseball (CBB)). Each sport has a relative search percentage for every designated market area in the US, plus the percent of Trump voters in each area.

The [data processing](https://github.com/STAT545-UBC-students/hw07-yavyx/blob/master/data-raw/data_processing.md) file details how the [raw data](https://github.com/STAT545-UBC-students/hw07-yavyx/blob/master/data-raw/NFL_fandom_data-google_trends.csv) was turned into a tidy dataset that loads automatically with the package.

The [vignette](https://github.com/STAT545-UBC-students/hw07-yavyx/blob/master/vignettes/using_sportspolitics.Rmd) shows how to use the package and its single function, `plot_sport()`.

##To Install
```{r}
library(devtools)
install_github("STAT545-UBC-students/hw07-yavyx")
```

This package requires `ggplot2` and `dplyr` to work, so make sure you load them too.

##Resources
The following pages where useful to develop this package.
---
title: "hw - 07 README"
author: "Javier Castillo-Arnemann"
output: github_document
---

This is a repository containing the 2nd assignment of the **STAT 547** course. The course main page can be found [here](http://stat545.com/Classroom). The instructions for this assignment can be accesed [here](http://stat545.com/Classroom/assignments/hw07/hw07.html).


##Package Information
For this homework I created a new data package called `sportsPolitics` that uses data from [FiveThirtyEight](https://fivethirtyeight.com/), a great politics, economics and sports blog that employs data analysis for all their articles. This dataset was used in their [How Every NFL Team's Fans Lean Politically](https://fivethirtyeight.com/features/how-every-nfl-teams-fans-lean-politically/) article, and summarizes the Google Trends results for Google searches of major sports in the US (NFL, MLB, NHL, NBA, College Football (CFB) and College Baseball (CBB)). Each sport has a relative search percentage for every designated market area in the US, plus the percent of Trump voters in each area.

The [data processing](https://github.com/STAT545-UBC-students/hw07-yavyx/blob/master/data-raw/data_processing.md) file details how the [raw data](https://github.com/STAT545-UBC-students/hw07-yavyx/blob/master/data-raw/NFL_fandom_data-google_trends.csv) was turned into a tidy dataset that loads automatically with the package.

The [vignette](https://github.com/STAT545-UBC-students/hw07-yavyx/blob/master/vignettes/using_sportspolitics.Rmd) shows how to use the package and its single function, `plot_sport()`.

##To Install
```{r}
library(devtools)
install_github("STAT545-UBC-students/hw07-yavyx")
```

This package requires `ggplot2` and `dplyr` to work, so make sure you load them too.

##Resources
- [Happy Git and GitHub for the useR, Chapter 18](http://happygitwithr.com/existing-github-last.html#connect-to-github)
- [Taking your data to go with R packages](http://www.davekleinschmidt.com/r-packages/)
- [R packages, raw data](http://r-pkgs.had.co.nz/data.html#data-extdata)
- [R packages, Object documentation](http://r-pkgs.had.co.nz/man.html)
- [Putting your R package on GitHub](http://kbroman.org/pkg_primer/pages/github.html)
- [STAT 547M Class Meetings 5 and 6: R Packages](http://stat545.com/Classroom/notes/cm105.nb.html#7_documentation_and_testing)

All these pages where useful to develop this package.
